---
title: "Untitled"
author: "kevin"
date: "December 29, 2020"
output: html_document
---
```{r}
data<- read.csv("activity.csv")
summary(data)
```

## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
steps_day<- with(data,tapply(steps,date,sum,na.rm=TRUE))
qplot(steps_day, xlab="total number of steps taken each day")
```
#mean steps taken per day
```{r}
mean(steps_day)
```
#median steps taken per day
```{r}
median(steps_day)
```
##What is the average daily activity pattern?
```{r warning=TRUE}
library(dplyr)
averages <- aggregate(x=list(steps=data$steps), by=list(interval=data$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(data=averages, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("average number of steps taken")
```
#Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
averages[which.max(averages$steps),]
```
## missing values
```{r}
sum(is.na(data$steps))
```
# Replace each missing value with the mean value of its 5-minute interval
```{r}
fill.value <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps))
        filled <- c(steps)
    else
        filled <- (averages[averages$interval==interval, "steps"])
    return(filled)
}
filled.data <- data
filled.data$steps <- mapply(fill.value, filled.data$steps, filled.data$interval)
```
## plot histogram
```{r}
total.steps <- tapply(filled.data$steps, filled.data$date, FUN=sum)
qplot(total.steps, binwidth=1000, xlab="total number of steps taken each day")
```
##  mean & median of total number of steps per day
```{r}
mean(total.steps)
median(total.steps)
```
## weekday and weekends 
```{r}
filled_data<- data
wekday<- function(date){
  day<-weekdays(date)
  if(day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday"))
    return("weekday")
  else if (day %in% c("Saturday","Sunday"))
    return("weekend")
  else
    stop("invalid date")
}
filled.data$date<- as.Date(filled.data$date)
filled.data$day<-sapply(filled.data$date, wekday)

```
##panel plot
```{r}
averages <- aggregate(steps ~ interval + day, data=filled.data, mean)
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) +
    xlab("5-minute interval") + ylab("Number of steps")
```